### 2012-10-16 papers/tevcat/sections/acknowledgements.tex
removed folder draft_v0
16/10/2012 : latest version with discussion and conclusion

The authors acknowledge the use of
HEALPix\footnote{\url{http://healpix.jpl.nasa.gov/}} \citep{healpix}.

>>>>

This research has made use of pywcsgrid2, an open-source plotting package for Python6\footnote{http://leejjoon.github.com/pywcsgrid2/}. The authors acknowledge the use of HEALPix\footnote{\url{http://healpix.jpl.nasa.gov/}} \citep{2005ApJ...622..759G}.

The authors acknowledge the use of the TeV catalog website\footnote{http://tevcat.uchicago.edu/} provided by the university of Chicago.

The authors acknowledge the use of the \emph{Australia Telescope National Facility} pulsar catalog\footnote{http://www.atnf.csiro.au/people/pulsar/psrcat/}.

### 2012-10-16 papers/tevcat/sections/method.tex
16/10/2012 : latest version with discussion and conclusion

\pointlike and \gtlike using two different shapes for the region of interest, we used all events contained in a disk of 5$\degr$ centered on the location of the TeV source when fitting the region with \pointlike and we used a $7\degr \times 7\degr$ square included in the previous disk when fitting the region using \gtlike. We tried to keep the two methods as close as possible by using the same conventions (same spatial binning : $\sim 0.06\degr/$bin, same energy binning : 8 energy bins per decade between 10~GeV and 316~GeV, same optimizer : MINUIT \citep{JamesRoos1975}).

@@

Sources within 10$\degr$ around each source of interest and listed in the hard source list \textbf{(cite the hard source list paper)} were included in our spatial-spectral model. We replaced potential TeV counterparts by a source with the TeV morphology summarized in Table \ref{tab:TeV_sources}. The spectral parameters of sources closer than 2$\degr$ to the source of interest were left free, while the parameters of all other sources were fixed at the hard source list (1FHL) catalog values.

Table \ref{tab:pulsars} summarizes the sources of our list located close to a pulsar detected by the \emph{Fermi}-LAT \textbf{cite 2PC}. The proximity of the pulsar can lead either to the non detection of a faint source hidden by the pulsed emission or to a contamination at low energy if the pulsar is not included. We decided to include in our analysis all the pulsars if they were outside of the TeV template or if they were more than 0.27$\degr$ away from the source of interest. Section \ref{puls_cont} will show the results for the sources close to the pulsars in the case were we added the pulsar in the model and fitted the TeV source.

@@

%Thus, we added the sources summarized in Tab. \ref{tab:newsources} to take these excesses into account. We fitted their spectra assuming a pure power--law above 10~GeV.

@@

\subsection{Analysis of the shape}

@@

As previously done in \cite{2012arXiv1207.0027L}, we only used radially-symmetric uniform disk shape (defined in Equation \ref{eq:Disk}) to fit the extension of the GeV emission. In the following, we quote the radius to the edge ($\sigma$) as the size of the source.

@@

\begin{eqnarray}
F(10-316 \, \rm GeV) = \int_{10 GeV}^{316 GeV} \frac{dN}{dE} dE\\
G(10-316 \, \rm GeV) = \int_{10 GeV}^{316 GeV} E \frac{dN}{dE} dE
\end{eqnarray}

@@

We measured the source significance using a test statistic (\text{TS}) defined as Equation \ref{eq:TS} , where $\mathcal{L}_1$ corresponds to the likelihood obtained by fitting a model of the source of interest and the background model and $\mathcal{L}_0$ corresponds to the likelihood obtained by fitting the background model only.

@@

We applied two criteria to decide if a source was significantly detected or not. We selected sources with a $\text{TS}$ above 16 (3.6 $\sigma$ with 2 d.o.f) when assuming the TeV morphology. Then, we applied a second filter on this list of sources by requiring $\text{TS}>16$ at the best GeV shape as well.

@@

The 56 regions summarized in Table~\ref{tab:TeV_sources} were all analyzed using the same procedure with both \gtlike and \pointlike:

@@

To take into account the modifications lead by our analysis and have a consistent analysis between all the regions studied, we performed a third iteration where we fixed the shape of the sources further than 2$\degr$ of the source of interest but included in our region to the best morphology found in this analysis (see section \ref{morph_res}). 
%Je n'arrive pas à être clair ici. Peut-etre ai-je fait une erreur. Pour que l'analyse soit cohérente et ne pas avoir une source modélisée d'une sorte dans une région et d'une autre sorte dans une autre région, j'ai retourné l'analyse en fixant les sources voisines non pas aux morphologies du 1FHL mais aux morphologies que j'ai trouvé. Par exemple la région de 1632 1634 a été tournée une première fois en ayant 1640 et 1616 aux morphologies inclues dans le 1FHL. Puis j'ai fait retourner la région avec 1640 et 1616 modélisé par les templates TeV).

For the significant sources ($\text{TS}_{TeV}>$16 and $\text{TS}_{GeV}>$16) we derived both the photon and energy fluxes inferred by the fit with the 1 sigma statistical errors, assuming the best morphology. When the source was not significant ($\text{TS}_{TeV}<$16 or $\text{TS}_{GeV}<$16), we derived a 99 \% Confidence Level (C.L.) Bayesian upper limit on the flux using a pure power-law model with an index fixed at 2, assuming the TeV shape.

\emph{Fermi}-LAT spectral points were obtained by splitting the 10--316 GeV range into 3 logarithmically spaced energy bins. A 99 \% C.L. upper limit is computed when $\text{TS}<$10 using the approach used by \cite{2012ApJS..199...31N}. The errors on the spectral points represent the statistical errors.

%This algorithm was used two times. During the first iteration we used the data selected in a $8\degr\times 8\degr$ square around the TeV position of the source of interest aligned with galactic coordinates. These region are extended enough to allow a reliable fit of the galactic diffuse template normalization \emph{ring\_2yearp7v6\_v0.fits}. In a second iteration we reduced the square to $4\degr\times4\degr$ and we fixed the galactic diffuse normalization to the value derived during the first iteration.\textbf{Develop}

%We launched a second iteration of this analysis with a smaller roi (4$\degr\times$4$\degr$) fixing the spectrum of the galactic background

@@

Two main systematic uncertainties can affect the extension fit of the sources: uncertainties in our model of the galactic diffuse emission and uncertainties on our knowledge of the LAT PSF.

@@

To estimate the uncertainties on the galactic diffuse emission, we used a GALPROP-based model and considered the various components of the diffuse emission model separately. We then individually fit the normalizations of each of them in our likelihood analysis. These various components are gamma-rays produced by IC emission, gamma-rays produced by interactions of CRs with atomic and ionized interstellar gas, and gamma-rays produced in the interactions of CRs with molecular gas. The model component describing the gamma-ray intensity from interactions with molecular gas is further subdivided into seven ranges of Galactocentric distance. It is not expected that this diffuse model is superior to the standard LAT model obtained through an all-sky fit. However, adding degrees of freedom to the background model can remove likely spurious sources that correlate with features in the Galactic diffuse emission. Therefore, this tests systematics that may be due to imperfect modeling of the diffuse emission in the region. This procedure was also used by \cite{2012arXiv1207.0027L}.

>>>>

\pointlike and \gtlike using two different shapes for the region of interest, we used all events contained in a disk of radius 5$\degr$ centered on the location of the TeV source when fitting the region with \pointlike and we used a $7\degr \times 7\degr$ square included in the previous disk when fitting the region using \gtlike. We tried to keep the two methods as close as possible by using the same conventions (same spatial binning : $\sim 0.06\degr/$bin, same energy binning : 8 energy bins per decade between 10~GeV and 316~GeV, same optimizer : MINUIT \citep{JamesRoos1975}).

@@

Sources within 10$\degr$ around each source of interest and listed in the hard source list \citep{1FHL} were included in our spatial-spectral model. We replaced potential TeV counterparts by a source with the TeV morphology summarized in Table \ref{tab:TeV_sources}. The spectral parameters of sources closer than 2$\degr$ to the source of interest were left free, while the parameters of all other sources were fixed at the hard source list (1FHL) catalog values \citep{1FHL}.

Table \ref{tab:pulsars} summarizes the sources of our list located close to a pulsar detected by the \emph{Fermi}-LAT \citep{2PC}. The proximity of the pulsar can lead either to the non detection of a faint source hidden by the pulsed emission or to a contamination at low energy if the pulsar is not included. We decided to include in our analysis all pulsars located outside of the TeV template or more than 0.27$\degr$ away from the source of interest, corresponding to the average PSF above 10 GeV. Section \ref{pulsarsect} will show the results for the sources close to the pulsars in the case where we added the pulsar in the model and fitted the TeV source.

@@

%Therefore, we added the sources summarized in Table \ref{tab:newsources} to take these excesses into account. We fitted their spectra assuming a pure power--law above 10~GeV.

@@

\subsection{Analysis of the shape}
\label{spatanalysis}

@@

As previously done in \cite{2012arXiv1207.0027L}, we only used a radially-symmetric uniform disk shape (defined in Equation \ref{eq:Disk}) to fit the extension of the GeV emission. In the following, we quote the radius to the edge ($\sigma$) as the size of the source.

@@

\begin{eqnarray}
F(10-316\text{ GeV}) = \int_{\text{10 GeV}}^{\text{316 GeV}} \frac{dN}{dE} dE\\
G(10-316\text{ GeV}) = \int_{\text{10 GeV}}^{\text{316 GeV}} E \frac{dN}{dE} dE
\label{energy_flux}
\end{eqnarray}

@@

We measured the source significance using a test statistic (\text{TS}) defined as Equation \ref{eq:TS}, where $\mathcal{L}_1$ corresponds to the likelihood obtained by fitting a model of the source of interest and the background model and $\mathcal{L}_0$ corresponds to the likelihood obtained by fitting the background model only.

@@

To decide if a source was significantly detected or not, we selected sources with a $\text{TS}$ above 16 (3.6 $\sigma$ with 2 d.o.f) when assuming the TeV morphology.

%We applied two criteria to decide if a source was significantly detected or not. We selected sources with a $\text{TS}$ above 16 (3.6 $\sigma$ with 2 d.o.f) when assuming the TeV morphology. Then, we applied a second filter on this list of sources by requiring $\text{TS}>16$ at the best GeV shape as well.

@@

The 58 regions summarized in Table~\ref{tab:TeV_sources} were all analyzed using the same procedure with both \gtlike and \pointlike:

@@

To have a self consistent analysis between all regions studied, we performed a third iteration where we used the best shape found in our pipeline for all sources located in the region of interest.

%To take into account the modifications lead by our analysis and have a consistent analysis between all the regions studied, we performed a third iteration where we fixed the shape of the sources further than 2$\degr$ of the source of interest but included in our region to the best morphology found in this analysis (see section \ref{morph_res}).

%Je n'arrive pas à être clair ici. Peut-etre ai-je fait une erreur. Pour que l'analyse soit cohérente et ne pas avoir une source modélisée d'une sorte dans une région et d'une autre sorte dans une autre région, j'ai retourné l'analyse en fixant les sources voisines non pas aux morphologies du 1FHL mais aux morphologies que j'ai trouvé. Par exemple la région de 1632 1634 a été tournée une première fois en ayant 1640 et 1616 aux morphologies inclues dans le 1FHL. Puis j'ai fait retourner la région avec 1640 et 1616 modélisé par les templates TeV).

For the significant sources ($\text{TS}_{TeV}>$16) we derived both the photon and energy fluxes inferred by the fit with the 1 sigma statistical errors, assuming the best morphology. When the source was not significant ($\text{TS}_{TeV}<$16), we derived a 99 \% Confidence Level (C.L.) Bayesian upper limit on the flux using a pure power-law model with an index fixed at 2, assuming the TeV shape.

\emph{Fermi}-LAT spectral points were obtained by splitting the 10--316 GeV range into 3 logarithmically spaced energy bins. A 99 \% C.L. upper limit is computed when $\text{TS}<$10 using the approach used by \cite{2012ApJS..199...31N}. The errors on the spectral points represent the statistic and systematic uncertainties as discussed below.

%This algorithm was used two times. During the first iteration we used the data selected in a $8\degr\times 8\degr$ square around the TeV position of the source of interest aligned with Galactic coordinates. These region are extended enough to allow a reliable fit of the Galactic diffuse template normalization \emph{ring\_2yearp7v6\_v0.fits}. In a second iteration we reduced the square to $4\degr\times4\degr$ and we fixed the Galactic diffuse normalization to the value derived during the first iteration.\textbf{Develop}

%We launched a second iteration of this analysis with a smaller roi (4$\degr\times$4$\degr$) fixing the spectrum of the Galactic background

@@

Two main systematic uncertainties can affect the extension fit of the sources: uncertainties in our model of the Galactic diffuse emission and uncertainties on our knowledge of the LAT PSF.

@@

To estimate the uncertainties on the Galactic diffuse emission, we used a GALPROP-based model and considered the various components of the diffuse emission model separately. We then individually fit the normalizations of each of them in our likelihood analysis. These various components are $\gamma$-rays produced by IC emission, $\gamma$-rays produced by interactions of CRs with atomic and ionized interstellar gas, and $\gamma$-rays produced in the interactions of CRs with molecular gas. The model component describing the $\gamma$-ray intensity from interactions with molecular gas is further subdivided into seven ranges of Galactocentric distance. It is not expected that this diffuse model is superior to the standard LAT model obtained through an all-sky fit. However, adding degrees of freedom to the background model can remove likely spurious sources that correlate with features in the Galactic diffuse emission. Therefore, this tests systematics that may be due to imperfect modeling of the diffuse emission in the region. This procedure was also used by \cite{2012arXiv1207.0027L}.

### 2012-10-16 papers/tevcat/tables.tex
16/10/2012 : latest version with discussion and conclusion

\tablecomments{ The first two columns are TeV source names and types as defined in the TeV catalog provided by the university of Chicago: PWN for Pulsar Wind Nebula, PSR for Pulsars, UNID for Unidentified sources, Massive Star Cluster and Star Forming Regions. The 3$^{rd}$ column reports the Galactic coordinates for each source. The 4$^{th}$ column presents the shape that best describes the source at TeV energies, together with a reference in the  5$^{th}$ column.}

@@

\clearpage
\begin{deluxetable}{llllc}
\tabletypesize{\scriptsize}
\tablecaption{List of sources with a pulsar within 0.5$\degr$
\label{tab:pulsars}}
\input{tables/pulsars.tex}\\
\begin{flushleft}
a- The distance between the pulsar and the source is lower than 0.27$\degr$.\\
b- The pulsar is located inside the edge of the TeV shape.\\
c- The pulsar shown no significant excess.\\
\end{flushleft}
\tablecomments{ $_{ }$List of sources having a known $\gamma$-ray pulsar within 0.5$\degr$. The two first column shows the TeV source and the pulsar name. The third column show the distance between the TeV source and the GeV pulsar. The pulsar position comes from \textbf{Citer 2PC}. In the fourth colum Y means that we added the pulsar to the model and N that we didn't added it.}

@@

\clearpage
\begin{landscape}
\begin{deluxetable}{lcccccc}
\tabletypesize{\scriptsize}
\tablecaption{Upper limits for non-detected TeV sources in three energy bands logarithmically-spaced between 10 and 316 GeV
\tabletypesize{\scriptsize}
\label{tab:nondet_sources2}}
\tablewidth{0pt}
\input{tables/undetected_energy_bin.tex}

@@

\tablecomments{Results of the maximum likelihood spectral fits  
for sources with a known $\gamma$-ray pulsar within 0.5 $\degr$. The pulsar is included in the model with the spectral parameters derived in the 2FGL catalog \cite{2012ApJS..199...31N}. A 99\% c.l. upper limit is computed when the TS is lower than 16. As PSR~J1028-5819 is already included and fitted in our model of the region of HESS J1026-5819 we did not report it in this table. PSR J1513-5908 and PSR J1702-4128 were detected after the 2FGL catalog analysis \citep{2012ApJS..199...31N}. Thus no spectral parameters were available.}

@@

>>>>

\tablecomments{The first two columns list the TeV source names and types as defined in the TeV catalog provided by the university of Chicago: PWN for Pulsar Wind Nebula, PSR for Pulsars, UNID for Unidentified sources, Massive Star Cluster and Star Forming Regions. The 3$^{rd}$ column reports the Galactic coordinates for each source. The 4$^{th}$ column presents the shape that best describes the source at TeV energies, together with a reference in the  5$^{th}$ column.}

@@

\clearpage
\begin{deluxetable}{llllc}
\tabletypesize{\scriptsize}
\tablecaption{List of sources with a pulsar within 0.5$\degr$
\label{tab:pulsars}}
\input{tables/pulsars.tex}\\
\begin{flushleft}
a- The distance between the pulsar and the source is lower than 0.27$\degr$.\\
b- The pulsar is located inside the edge of the TeV shape.\\
c- No significant excess above 10 GeV at the position of the pulsar.\\
\end{flushleft}
\tablecomments{ $_{ }$List of sources having a known $\gamma$-ray pulsar within 0.5$\degr$. The two first columns list the TeV source and the pulsar name. The third column gives the distance between the TeV source and the GeV pulsar. The pulsar position comes from \cite{2PC}. In the fourth colum Y means that we added the pulsar to the model and N that we didn't added it.}

@@

\clearpage
\begin{landscape}
\begin{deluxetable}{lcccccc}
\tabletypesize{\scriptsize}
\tablecaption{Upper limits for non-detected sources in 3 logarithmically-spaced energy bands
\tabletypesize{\scriptsize}
\label{tab:nondet_sources2}}
\tablewidth{0pt}
\input{tables/undetected_energy_bin.tex}

@@

\tablecomments{Results of the maximum likelihood spectral fits for sources with a known $\gamma$-ray pulsar within 0.5$\degr$. The pulsar is included in the model with the spectral parameters derived in the 2FGL catalog \cite{2012ApJS..199...31N}. A 99\% c.l. upper limit is computed when the TS is lower than 16. As PSR~J1028-5819 is already included and fitted in our model of the region of HESS J1026-5819 we did not report it in this table. PSR J1513-5908 and PSR J1702-4128 were detected after the 2FGL catalog analysis \citep{2012ApJS..199...31N}. Therefore no spectral parameters were available for these 2 pulsars.}

\end{deluxetable}
\normalsize
\noindent
\clearpage

\begin{deluxetable}{llcccc}
\tabletypesize{\scriptsize}
\tablecaption{Pulsars characteristics.
\tabletypesize{\scriptsize}
\label{tab:table_luminosity}}
\tablewidth{0pt}
\input{tables/table_luminosity.tex}\\

\tablecomments{This table summarizes the pulsars properties taken into account in this analysis to perform the populations studies in Figures \ref{fig:dotelpwn} \& \ref{fig:rapportX}. Column 3 shows the pulsar spin-down power as found in the litterature, column 4 and 5 present the characteristic age of the pulsar and its distance.\\References: (1) \cite{1973PASP...85..579T}, (2) \cite{2008MNRAS.389.1881K}, (3) \cite{2004MNRAS.352.1405C}, (4) \cite{dalton1303}, (5) \cite{2005yCat.7245....0M}, (6) \cite{2006MNRAS.372..777L}, (7) \cite{1997ApJ...476..347Y}, (8) \cite{2012ApJ...750..162K}, (9) \cite{2009ApJ...694...12M}, (10) \cite{1996ApJ...471..887S}, (11) \cite{1999ApJ...511..274S}, (12) \cite{2007ApJ...662..517F}, (13) \cite{2003MNRAS.342.1299K}, (14) \cite{1995A&A...293..795J},  (15) \cite{2001MNRAS.328...17M}, (16) \cite{2011ICRC....7..247H}, (17) \cite{2006ApJ...637..456C}, (18) \cite{2012ApJ...755L..20P}, (19) \cite{2008AIPC.1085..372C}, (20) \cite{2011ApJ...729L..16G}, (21) \cite{2010ApJ...708.1426W}, (22) \cite{2012ApJ...755...39V}, (23) \cite{1997ApJ...476..347Y}, (24) \cite{2004ApJ...612..389H}, (25) \cite{2009ApJ...706.1331A}, (26) \cite{2001ApJ...560..236K}, (27) \cite{1993AJ....105.1060P}, (28) \cite{2008AJ....136.1477L}, (29) \cite{2003ApJ...596.1137D}, (30) \cite{2010ApJ...725..571S}, (31) \cite{2009ApJ...691..895T}, (32) \cite{2010A&A...520A.111B}.}

@@

\normalsize
\noindent
\clearpage

\begin{deluxetable}{llccccc}
\tabletypesize{\scriptsize}
\tablecaption{PWNe properties.
\tabletypesize{\scriptsize}
\label{tab:table_luminosity2}}
\tablewidth{0pt}
\input{tables/table_luminosity_2.tex}\\

\tablecomments{This table summarizes the PWNe properties and the fluxes taken into account in this analysis to perform the populations studies in Figures \ref{fig:dotelpwn} \& \ref{fig:rapportX}. Column 2,3 and 4 summarize the fluxes found in the GeV (10-316 GeV) , TeV (1-30 TeV) and X-ray (2-10 keV) energy ranges. Column 5 shows the luminosity found using the energy flux in column 2 and the distance in Table \ref{tab:table_luminosity}. \\References : (1) \cite{2009ApJ...694...12M} and references therein, (2) \cite{2011AA...525A..46H}, (3) \cite{Mayerdiploma}, (4) \cite{2011AA...533A.103H}, (5) \cite{2012arXiv1205.0719D}, (6) \cite{2010A&A...520A.111B}, (7) \cite{2006ApJ...636..777A}, (8) \cite{2011arXiv1112.2901H}, (9) \cite{2008AA...477..353A}, (10) \cite{2008AIPC.1085..372C}, (11) \cite{2008AIPC.1085..312T}, (12) \cite{dalton1303}, (13) \cite{2012ApJ...750..162K}, (14) \cite{2009ApJ...691..895T}.}

\end{deluxetable}
\normalsize
\noindent
\clearpage

\begin{deluxetable}{lcccc}
\tabletypesize{\scriptsize}
\tablecaption{Results of the fit of the IC peak.
\tabletypesize{\scriptsize}
\label{tab:Epeak}}
\tablewidth{0pt}
\input{tables/Epeak.tex}\\
\tablecomments{}
\end{deluxetable}
\normalsize
\noindent
